Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-06-30 edubots_surveys.Rnw
removes No/NA values from data

\address[id=aff1]{%                           % unique id
  \orgdiv{Department of Computer Architecture and Technology},             % department, if any
  \orgname{University of Granada},          % university, etc
  \city{Granada},                              % city
  \cny{Spain}                                    % country
}
\address[id=aff2]{%
  \orgdiv{Department of Signal Theory, Telematics and Communications},
  \orgname{University of Granada},          % university, etc
  \city{Granada},                              % city
  \cny{Spain}                                    % country
}

\address[id=aff3]{%
  \orgdiv{School of Computing},
  \orgname{University of Leeds},          % university, etc
  \city{Leeds},                              % city
  \cny{UK}                                    % country
}

\address[id=aff4]{%
  \orgname{CYENS},          % university, etc
  \city{Nicosia},                              % city
  \cny{Cyprus}                                    % country
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter short notes here                   %%
%%                                          %%
%% Short notes will be after addresses      %%
%% on first page.                           %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

survey.pilot %>%  mutate(Messaging.Organization =str_split(Messaging.Organization, ", ")) %>% unnest(cols = c(Messaging.Organization)) -> survey.pilot.MessagingOrganization

survey.pilot %>% group_by( PostCOVID.changes ) %>% filter( n() > 1 ) -> survey.pilot.postCOVID

survey.pilot %>%  mutate(ChatbotType = ifelse(AgendaBot == "No","","AgendaBot,")) %>%
  mutate(ChatbotType = ifelse(ClassMaterialBot == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "ClassMaterialBot,",sep=""))) %>%
  mutate(ChatbotType = ifelse(FAQBot == "No",paste(ChatbotType, "",sep=""), paste(ChatbotType, "FAQBot,",sep=""))) %>%
  mutate(ChatbotType = ifelse(GradesBot == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "GradesBot,",sep=""))) %>%
  mutate(ChatbotType = ifelse(OtherBot == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "OtherBot,",sep=""))) %>%
  mutate(ChatbotType = substr(ChatbotType,1,nchar(ChatbotType)-1))-> survey.pilot.chatbottype
survey.pilot.chatbottype %>%  mutate(ChatbotType =str_split(ChatbotType, ",")) %>% unnest(cols = c(ChatbotType)) -> survey.pilot.ChatbotType

@@

survey.interaction <- read.csv("data/survey-student-interaction-pilot-3-2021-EN.csv")
survey.interaction %>% group_by( Gender ) %>% summarise ( n = n() ) %>% mutate( freqGender = n/sum(n)) -> freqInteraction.Gender
survey.interaction %>% group_by( Age ) %>% summarise ( n = n() ) %>% mutate( freqAge = n/sum(n)) -> freqInteraction.Age
survey.interaction %>% group_by( Experience ) %>% summarise ( n = n() ) %>% mutate( freqExperience = n/sum(n)) -> freqInteraction.Experience

@@

\begin{figure}[h!tbp]
\begin{center}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<gender, echo=FALSE, fig.width=3.2, fig.height=2.5>>=
#ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
freq.Gender$source<-rep("survey1")
freqInteraction.Gender$source<-rep("survey2")
freqbinded.Gender <- rbind(freq.Gender, freqInteraction.Gender)
freqbinded.Gender$source <- factor(freqbinded.Gender$source) 
ggplot(freqbinded.Gender, aes(x = Gender, y=freqGender, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/gender.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<age,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
#ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
freq.Age$source<-rep("survey1")
freqInteraction.Age$source<-rep("survey2")
freqbinded.Age <- rbind(freq.Age, freqInteraction.Age)
freqbinded.Age$source <- factor(freqbinded.Age$source) 
ggplot(freqbinded.Age, aes(x = Age, y=freqAge, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/age.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<sector,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
#ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
freq.Sector$source<-rep("survey1")
freqInteraction.Sector$source<-rep("survey2")
freqbinded.Sector <- rbind(freq.Sector, freqInteraction.Sector)
freqbinded.Sector$source <- factor(freqbinded.Sector$source) 
ggplot(freqbinded.Sector, aes(x = Sector, y=freqSector, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/sector.pdf}
    \end{minipage}
    \vspace{0.5mm}
    \begin{minipage}[t]{0.38\textwidth}
        \centering
<<experience, echo=FALSE, fig.width=4.5, fig.height=3.475>>=
#ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
freq.Experience$source<-rep("survey1")
freqInteraction.Experience$source<-rep("survey2")
freqbinded.Experience <- rbind(freq.Experience, freqInteraction.Experience)
freqbinded.Experience$source <- factor(freqbinded.Experience$source) 
ggplot(freqbinded.Experience, aes(x = Experience, y=freqExperience, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
@        
%       \includegraphics[width=\textwidth]{figures/experience.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.52\textwidth}
        \centering
<<discipline,echo=FALSE, fig.width=8.2, fig.height=4.45>>=
#ggplot(freq.Discipline, aes(x=Discipline, y=freqDiscipline, fill=Discipline)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
freq.Discipline$source<-rep("survey1")
freqInteraction.Discipline$source<-rep("survey2")
freqbinded.Discipline <- rbind(freq.Discipline, freqInteraction.Discipline)
freqbinded.Discipline$source <- factor(freqbinded.Discipline$source) 
freqbinded.Discipline$Discipline <- factor(freqbinded.Discipline$Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other"))
ggplot(freqbinded.Discipline, aes(x = Discipline, y=freqDiscipline, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
@

@@

\begin{figure}[h!tbp]
\begin{center}
    \begin{minipage}[t]{0.31\textwidth}
        \centering
<<gender_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.pilot, aes(x = MessagingPlatformProvided, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/gender_provided.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.31\textwidth}
        \centering
<<experience_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.pilot, aes(x = MessagingPlatformProvided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
@       
%       \includegraphics[width=\textwidth]{figures/experience_provided.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.31\textwidth}
        \centering
<<sector_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.pilot, aes(x = MessagingPlatformProvided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
@       
%       \includegraphics[width=\textwidth]{figures/sector_provided.pdf}
    \end{minipage}
    %----
    \vspace{0.2mm}
    \hspace{10mm}
    \begin{minipage}[t]{0.5\textwidth}
        \centering
<<discipline_provided, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=

@@

ggplot(survey.pilot, aes(x = MessagingPlatformWhatsApp, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())

@@

ggplot(survey.pilot, aes(x = MessagingPlatformWhatsApp, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())

@@

ggplot(survey.pilot, aes(x = MessagingPlatformTelegram, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())

@@

ggplot(survey.pilot, aes(x = MessagingPlatformTelegram, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())

@@

    \multicolumn{1}{|l|}{University} & 5.71\% & 0.56\% & 0.04\%  &  \textbf{25.26\%}\\ \hline

@@

    \multicolumn{1}{|l|}{Vocational} & 12.38\% & 1.21\% & 0.08\% & \textbf{54.78\%}\\ \hline

@@

    \multicolumn{1}{|l|}{Biomed/Sciences} & 3.50\% &  2.50\% & 9.94\% & 1.75\% \\ \hline

@@

    \multicolumn{1}{|l|}{Hum/Social} &  15.55\% & \textbf{19.19\%} &  11.04\% & 0.01\%\\ \hline

@@

    \multicolumn{1}{|l|}{Tech/Engineering} &  11.06\% &  11.76\% &  \textbf{13.29\%} & 0.40\%\\ \hline

>>>>

\address[id=aff1]{%                           % unique id
  \orgdiv{Department of Computer Architecture and Technology},             % department, if any
  \orgname{University of Granada},          % university, etc
  \city{Granada},                              % city
  \cny{Spain}                                    % country
}
\address[id=aff2]{%
  \orgdiv{Department of Signal Theory, Telematics and Communications},
  \orgname{University of Granada},          % university, etc
  \city{Granada},                              % city
  \cny{Spain}                                    % country
}
\address[id=aff3]{%
  \orgdiv{School of Computing},
  \orgname{University of Leeds},          % university, etc
  \city{Leeds},                              % city
  \cny{UK}                                    % country
}
\address[id=aff4]{%
  \orgname{CYENS},          % university, etc
  \city{Nicosia},                              % city
  \cny{Cyprus}                                    % country
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter short notes here                   %%
%%                                          %%
%% Short notes will be after addresses      %%
%% on first page.                           %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

survey.pilot %>%  mutate(Messaging.Organization =str_split(Messaging.Organization, ", ")) %>% unnest(cols = c(Messaging.Organization)) -> survey.pilot.MessagingOrganization
survey.pilot.MessagingOrganization[as.character(survey.pilot.MessagingOrganization$Messaging.Organization)!="No", ] -> survey.pilot.MessagingOrganization

survey.pilot %>% group_by( PostCOVID.changes ) %>% filter( n() > 1 ) -> survey.pilot.postCOVID
survey.pilot.postCOVID[as.character(survey.pilot.postCOVID$PostCOVID.changes)!="No", ] -> survey.pilot.postCOVID

survey.pilot %>%  mutate(ChatbotType = ifelse(AgendaBot == "No","","AgendaBot,")) %>%
  mutate(ChatbotType = ifelse(ClassMaterialBot == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "ClassMaterialBot,",sep=""))) %>%
  mutate(ChatbotType = ifelse(FAQBot == "No",paste(ChatbotType, "",sep=""), paste(ChatbotType, "FAQBot,",sep=""))) %>%
  mutate(ChatbotType = ifelse(GradesBot == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "GradesBot,",sep=""))) %>%
  mutate(ChatbotType = ifelse(OtherBot == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "OtherBot,",sep=""))) %>%
  mutate(ChatbotType = substr(ChatbotType,1,nchar(ChatbotType)-1))-> survey.pilot.chatbottype
survey.pilot.chatbottype %>%  mutate(ChatbotType =str_split(ChatbotType, ",")) %>% unnest(cols = c(ChatbotType)) -> survey.pilot.ChatbotType
survey.pilot.ChatbotType[as.character(survey.pilot.ChatbotType$Gender)!="No", ] -> survey.pilot.ChatbotType
survey.pilot.ChatbotType[as.character(survey.pilot.ChatbotType$Experience)!="No", ] -> survey.pilot.ChatbotType

@@

survey.interaction <- read.csv("data/survey-student-interaction-pilot-3-2021-EN.csv")
survey.interaction[as.character(survey.interaction$Discipline)!="No", ] -> survey.interaction
survey.interaction %>% group_by( Gender ) %>% summarise ( n = n() ) %>% mutate( freqGender = n/sum(n)) -> freqInteraction.Gender
survey.interaction %>% group_by( Age ) %>% summarise ( n = n() ) %>% mutate( freqAge = n/sum(n)) -> freqInteraction.Age
survey.interaction %>% group_by( Experience ) %>% summarise ( n = n() ) %>% mutate( freqExperience = n/sum(n)) -> freqInteraction.Experience

@@

\begin{figure}[h!tbp]
\begin{center}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<gender, echo=FALSE, fig.width=3.2, fig.height=2.5>>=
#ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
freq.Gender$source<-rep("survey1")
freqInteraction.Gender$source<-rep("survey2")
freqbinded.Gender <- rbind(freq.Gender, freqInteraction.Gender)
freqbinded.Gender$source <- factor(freqbinded.Gender$source) 
freqbinded.Gender[as.character(freqbinded.Gender$Gender)!="No", ] -> df1
ggplot(df1, aes(x = Gender, y=freqGender, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/gender.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<age,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
#ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
freq.Age$source<-rep("survey1")
freqInteraction.Age$source<-rep("survey2")
freqbinded.Age <- rbind(freq.Age, freqInteraction.Age)
freqbinded.Age$source <- factor(freqbinded.Age$source) 
freqbinded.Age[as.character(freqbinded.Age$Age)!="No", ] -> df1
ggplot(df1, aes(x = Age, y=freqAge, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/age.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<sector,echo=FALSE, fig.width=3.2, fig.height=2.5>>=
#ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
freq.Sector$source<-rep("survey1")
freqInteraction.Sector$source<-rep("survey2")
freqbinded.Sector <- rbind(freq.Sector, freqInteraction.Sector)
freqbinded.Sector$source <- factor(freqbinded.Sector$source) 
ggplot(freqbinded.Sector, aes(x = Sector, y=freqSector, fill = source)) + geom_bar(stat="identity", position = "dodge")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/sector.pdf}
    \end{minipage}
    \vspace{0.5mm}
    \begin{minipage}[t]{0.38\textwidth}
        \centering
<<experience, echo=FALSE, fig.width=4.5, fig.height=3.475>>=
#ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
freq.Experience$source<-rep("survey1")
freqInteraction.Experience$source<-rep("survey2")
freqbinded.Experience <- rbind(freq.Experience, freqInteraction.Experience)
freqbinded.Experience$source <- factor(freqbinded.Experience$source) 
freqbinded.Experience[as.character(freqbinded.Experience$Experience)!="No", ] -> df1
ggplot(df1, aes(x = Experience, y=freqExperience, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
@        
%       \includegraphics[width=\textwidth]{figures/experience.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.52\textwidth}
        \centering
<<discipline,echo=FALSE, fig.width=8.2, fig.height=4.45>>=
#ggplot(freq.Discipline, aes(x=Discipline, y=freqDiscipline, fill=Discipline)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
freq.Discipline$source<-rep("survey1")
freqInteraction.Discipline$source<-rep("survey2")
freqbinded.Discipline <- rbind(freq.Discipline, freqInteraction.Discipline)
freqbinded.Discipline$source <- factor(freqbinded.Discipline$source) 
freqbinded.Discipline$Discipline <- factor(freqbinded.Discipline$Discipline, levels = c("Biomedicine", "Humanities", "Social Sciences", "Sciences", "Tech/Engineering", "Other"))
ggplot(freqbinded.Discipline, aes(x = Discipline, y=freqDiscipline, fill = source)) + geom_bar(stat="identity", position = "dodge", show.legend = FALSE)+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank())
@

@@

\begin{figure}[h!tbp]
\begin{center}
<<gender_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
survey.pilot[as.character(survey.pilot$Gender)!="No", ] -> df1
ggplot(df1, aes(x = MessagingPlatformProvided, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
%       \includegraphics[width=\textwidth]{figures/gender_provided.pdf}
<<experience_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
ggplot(df1, aes(x = MessagingPlatformProvided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
%       \includegraphics[width=\textwidth]{figures/experience_provided.pdf}
<<sector_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.pilot, aes(x = MessagingPlatformProvided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
%       \includegraphics[width=\textwidth]{figures/sector_provided.pdf}
<<discipline_provided, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=

@@

survey.pilot[as.character(survey.pilot$Gender)!="No", ] -> df1
ggplot(df1, aes(x = MessagingPlatformWhatsApp, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())

@@

survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
ggplot(df1, aes(x = MessagingPlatformWhatsApp, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())

@@

survey.pilot[as.character(survey.pilot$Gender)!="No", ] -> df1
ggplot(df1, aes(x = MessagingPlatformTelegram, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())

@@

survey.pilot[as.character(survey.pilot$Experience)!="No", ] -> df1
ggplot(df1, aes(x = MessagingPlatformTelegram, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())

@@

    \multicolumn{1}{|l|}{} & 5.71\% & 0.56\% & 0.04\%  &  \textbf{25.26\%}\\ \hline

@@

    \multicolumn{1}{|l|}{} & 12.38\% & 1.21\% & 0.08\% & \textbf{54.78\%}\\ \hline

@@

    \multicolumn{1}{|l|}{} & 3.50\% &  2.50\% & 9.94\% & 1.75\% \\ \hline

@@

    \multicolumn{1}{|l|}{} &  15.55\% & \textbf{19.19\%} &  11.04\% & 0.01\%\\ \hline

@@

    \multicolumn{1}{|l|}{} &  11.06\% &  11.76\% &  \textbf{13.29\%} & 0.40\%\\ \hline
